K2 Analysis

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

To test whether the effect of \textsc{Condition} could be due to the
relatively high number of \emph{false} responses in the
\es-conditions, we regrouped the factor \textsc{Response} once more to
distinguish only \emph{local} responses from \emph{other}
responses. Doing so allows us to address the question whether the
amount of \emph{local} responses differed across conditions and
accentuation types. But this does not seem to be the case. The
smallest model that predicts the data well in this case contains
factors \textsc{Response} and \textsc{Position} and their two-way
interaction.

>>>>

To test whether the effect of \textsc{Condition} could be due to the
relatively high number of \emph{false} responses in the
\es-conditions, we regrouped the factor \textsc{Response} once more to
distinguish only \emph{local} responses from \emph{other}
responses. Doing so allows us to address the question whether the
amount of \emph{local} responses differed across conditions and
accentuation types. But this does not seem to be the case. The
smallest model that predicts the data well in this case contains
factors \textsc{Response} and \textsc{Position} and their two-way
interaction ($\chi^2 = 4.71$, $df=18$, $p = 0.999$, $AIC = 16.711$
(compared to $AIC=48$ of the saturated model)). This suggests that a
shift in the distribution of \emph{local} responses can be
satisfactorily explained as a position effect across conditions: later
trials yielded less \emph{other} responses.

To test, then, whether this prediction is the result of an decrease of
\emph{false} responses in later trials or an actual shift in the
distribution between \emph{literal} and \emph{local} distribution, we
also computed the best log-linear predictor for the subset of our data
including only \emph{literal} and \emph{local} responses. Doing so,
the best predictor indeed drops factor \textsc{Position} and contains
only factors \textsc{Response} and \textsc{Condition} and their
two-way interaction ($\chi^2 = 12.497$, $df=20$, $p = 0.898$, $AIC =
20.497$ (compared to $AIC=48$ of the saturated model)). This suggests
that the factor \textsc{Position} is not relevant for explaining the
distribution of \emph{literal} and \emph{local} readings. Its effects
noted previously are most likely due to the decrease of \emph{false}
responses in later trials of the \es-conditions.
